---
title: "Home"
---

Welcome to the Forecasting Lake and Reservoir Ecosystems (FLARE) dashboard!

This page was last updated on `r Sys.Date()`

This dashboard provides daily updates to visualize recent water quality forecasts generated across the world using FLARE system. FLARE iterative updates model simulations using real-time data and quantifies uncertainty in forecasts.

### FLARE sites

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, include=FALSE)
```

```{r, setup}
library(ggiraph)
library(patchwork)
library(tidyverse)
library(neon4cast)
library(score4cast)
library(thematic)
thematic_rmd(bg="white", fg="black", accent="blue")
```

```{r}
library(sf)
library(tmap)
library(jsonlite)
library(dplyr)

neon <- sf::st_read("sites.json")
```

```{r fig.height=5, fig.width=5, echo=FALSE, include=TRUE}
tmap::tmap_mode("view")
neon  |> #-149.610636, 68.630692
  tm_shape(bbox=c(-260,-35.436808, 0, 68.630692)) + 
  tm_bubbles(col="Partner", size = 0.2, popup.vars = c("site_id"), jitter =TRUE) 
```

This material is based upon work supported by the National Science Foundation as part of awards CNS-1737424, DBI-1933102, and DBI-1933016​. Any opinions, findings, and conclusions or recommendations expressed in this material are those of the author(s) and do not necessarily reflect the views of the National Science Foundation.
