---
title: "Home"
---

Welcome to the Forecasting Lake and Reservoir Ecosystems (FLARE) dashboard!

This page was last updated on `r lubridate::with_tz(Sys.time(), tzone = "America/New_York")`

This dashboard provides daily updates to visualize recent water quality forecasts generated across the world using FLARE systems that iterative updates model simulations using real-time data and quantifies uncertainty in forecasts.

### FLARE sites

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, include=FALSE)
```

```{r, setup}
library(ggiraph)
library(patchwork)
library(tidyverse)
library(neon4cast)
library(score4cast)
library(thematic)
thematic_rmd(bg="white", fg="black", accent="blue")
```

```{r}
library(sf)
library(tmap)
library(jsonlite)
library(dplyr)

if (!file.exists("neon.json")) {
  
  # scale by number of teams submitting forecast at a given site
  challenges <- 
    neon4cast::combined_scores(collect=FALSE) |>
    select(site_id, model_id) |>
    distinct() |>
    count(site_id) |> 
    collect()

  geo <- read_json("https://github.com/eco4cast/neon4cast/raw/main/inst/extdata/neon_geo.json", TRUE)
  site_id <- gsub(", .*$", "", geo$geographicDescription)
  bb <- geo$boundingCoordinates[1:4] |>
    mutate_all(as.numeric) |> 
    mutate(site_id = site_id)
  bb <- inner_join(bb, challenges, by = "site_id")
  neon <- st_as_sf(bb, 
                   coords = c("westBoundingCoordinate",
                              "northBoundingCoordinate"),
                   crs = 4326) |> 
    select(-eastBoundingCoordinate,
           -southBoundingCoordinate) #|>
    #rename(theme = target_id)
  #neon2 <- neon |>
  #  tidyr::pivot_wider(names_from = "theme", values_from = site_id) |> 
  #  rename(terrestrial = terrestrial_daily) |> 
  #  select(-terrestrial_30min) |> 
  #  st_as_sf()
  
  sf::st_write(neon, "neon.json", driver="GeoJSON")
} else {
  neon <- sf::st_read("neon.json")
}
```

```{r fig.height=5, fig.width=5, echo=FALSE, include=TRUE}
tmap::tmap_mode("view")
neon  |>
  tm_shape(bbox=c(139.168997,-35.436808,-74,48)) + 
  tm_bubbles(col="Partner", popup.vars = c("site_id"), jitter =TRUE) 
```


This material is based upon work supported by the National Science Foundation as part of awards CNS-1737424, DBI-1933102, and DBI-1933016​. Any opinions, findings, and conclusions or recommendations expressed in this material are those of the author(s) and do not necessarily reflect the views of the National Science Foundation.
