---
title: "Home"
---

Welcome to the Forecasting Lake and Reservoir Ecosystems (FLARE) dashboard!

This page was last updated on `r Sys.Date()`

This dashboard provides daily updates to visualize recent water quality forecasts generated across the world using FLARE system. FLARE iterative updates model simulations using real-time data and quantifies uncertainty in forecasts.

### FLARE sites

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, include=FALSE)
```

```{r, setup}
library(ggiraph)
library(patchwork)
library(tidyverse)
library(neon4cast)
library(score4cast)
library(thematic)
thematic_rmd(bg="white", fg="black", accent="blue")
```

```{r}
library(sf)
library(tmap)
library(jsonlite)
library(dplyr)
library(leaflet)

neon <- sf::st_read("sites.json")
```

```{r fig.height=5, fig.width=5, echo=FALSE, include=TRUE, }
leaflet() %>%
  #setView(lat = 37.2296, lng = -100, zoom=2) %>%
  addTiles(group="OSM") %>%
  addProviderTiles(providers$Esri.WorldTopoMap, group="Topo Map") %>%
  addProviderTiles(providers$Esri.WorldImagery, group="Imagery") %>%
  addLayersControl(baseGroups=c('OSM', 'Topo Map','Imagery')) |> 
  addMarkers(data  = neon, popup=~as.character(site_id), group = ~as.character(Partner), clusterOptions = markerClusterOptions())

```

This material is based upon work supported by the National Science Foundation as part of awards CNS-1737424, DBI-1933102, and DBI-1933016​. Any opinions, findings, and conclusions or recommendations expressed in this material are those of the author(s) and do not necessarily reflect the views of the National Science Foundation.
