---
title: "North Temperate Lakes - LTER"
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```

```{r setup}
library(ggiraph)
library(patchwork)
library(tidyverse)
library(neon4cast)
library(score4cast)


library(thematic)
thematic_rmd(bg="white", fg="black", accent="blue")

source("R/flare-plots.R")
source("R/ignore_sigpipes.R")
```

## Most Recent Forecasts

The [North Temperate Lakes Long-Term Ecological Research (NTL-LTER)](https://lter.limnology.wisc.edu) program conducts and facilitates long-term ecological research on Wisconsin lakes. Housed on both the University of Wisconsin-Madison campus and at Trout Lake Station, NTL is part of the larger LTER network funded by the U.S. National Science Foundation since 1981.

NTL forecasts are generated in collaboration with scientists from NTL at the UW Center for Limnology (Noah Lottig, Paul Schramm, and Paul Hanson).

::: panel-tabset
## Sparkling Lake

```{r}
s3_score <- arrow::s3_bucket(bucket = "bio230121-bucket01/flare/scores/parquet", endpoint_override = "amnh1.osn.mghpcc.org", anonymous = TRUE)
s3_forecast <- arrow::s3_bucket(bucket = "bio230121-bucket01/flare/forecasts/parquet", endpoint_override = "amnh1.osn.mghpcc.org", anonymous = TRUE)
  
most_recent <-  arrow::open_dataset(s3_score) |> 
  filter(site_id %in% c("SPLK")) |> 
  summarize(max = max(reference_datetime)) |> 
  collect() |> 
  pull()

df_insitu_scores <- arrow::open_dataset(s3_score) |>
  filter(variable == "temperature",
         # depth %in% c(0.5),
         site_id %in% c("SPLK"),
         reference_datetime == most_recent) |>
  dplyr::collect()
```

The most recent forecast is from `r lubridate::with_tz(lubridate::as_datetime(most_recent), tzone = "America/New_York")` (Eastern U.S. time).

```{r splk-temp}
df_insitu_scores_lake <- df_insitu_scores |> 
  filter(site_id == "SPLK")

plot_temp(df_insitu_scores_lake, depths = c(1,8)) 
```

```{r splk-depth, eval=F}
# depth plot
depth_scores <- arrow::open_dataset(s3_score) |> 
  filter(variable == "depth",
         site_id %in% c("SPLK"),
         reference_datetime == most_recent) |> 
  dplyr::collect()

plot_depth(depth_scores) 
```

```{r splk-mixing}
s3_splk <- arrow::s3_bucket(bucket = "bio230121-bucket01/flare/forecasts/parquet/site_id=SPLK/model_id=glm_flare_v1", endpoint_override = "amnh1.osn.mghpcc.org", anonymous = TRUE)

# chance of being mixed
temperature_forecast <- arrow::open_dataset(s3_splk, unify_schemas = FALSE) |> 
  filter(variable == "temperature",
         #site_id %in% c("SPLK"),
         reference_datetime == most_recent) |> 
  dplyr::collect() 

plot_mixing(forecast_df = temperature_forecast, eval_depths = c(1, 8), use_density = T, threshold = 0.1)

```

```{r splk-ice}
# Ice plot
ice_forecasts <- arrow::open_dataset(s3_splk, unify_schemas = TRUE) |> 
  filter(variable == "ice_thickness",
         #site_id %in% c("SPLK"),
         reference_datetime == most_recent) |> 
  dplyr::collect()

plot_ice(ice_forecasts)
```
:::
